Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States

### 2017-11-08 doc/manuscript/manuscript.Rmd
acknowledge contributors and add link to interactive vis for #15

The authors would like to thank Rebecca Higgens for technical support in generating the data for the MCG assessment, aggressiveness ratings, and genotyping; and for providing valuable insights into the historical context of the data collection and curation.

@@

![
Graph showing complex associations between Mycelial Compatibility Groups (MCG) (dotted nodes) and Multilocus Haplotypes (MLH) (full nodes) where the number in each node represents the MLH/MCG assignment. 
Node size reflect the number of samples represented by each node (circle). 
Edges (arrows) point from MLH to MCG where the weight (thickness) of the edge represents the number of samples shared. 
Node color represents the community assignment based on the walktrap algorithm with a maximum of four steps [@pons2006computing]. 
](../../results/figures/publication/full-graph.pdf){#fullgraph width=100%}

>>>>

The authors would like to thank Rebecca Higgens for technical support in generating the data for the MCG assessment, aggressiveness ratings, and genotyping; and for providing valuable insights into the historical context of the data collection and curation. 
We would also like to thank Denita Hadziabdic and two anonymous reviewers for their valuable comments and insights that improved the quality of the manuscript.

@@

![
Graph showing complex associations between Mycelial Compatibility Groups (MCG) (dotted nodes) and Multilocus Haplotypes (MLH) (full nodes) where the number in each node represents the MLH/MCG assignment. 
Node size reflect the number of samples represented by each node (circle). 
Edges (arrows) point from MLH to MCG where the weight (thickness) of the edge represents the number of samples shared. 
Node color represents the community assignment based on the walktrap algorithm with a maximum of four steps [@pons2006computing]. 
An interactive version of this network can be recreated using the code in the "Interactive visualizations" section of the mlg-mcg.md file in the supplementary information (Direct Link: https://github.com/everhartlab/sclerotinia-366/blob/master/results/mlg-mcg.md#interactive-visualizations)  [@kamvar2017data].
](../../results/figures/publication/full-graph.pdf){#fullgraph width=100%}
